---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(researchr)
install.packages("webshot")
webshot::install_phantomjs()
```

# researchr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/kbruncati)](https://CRAN.R-project.org/package=researchr)
<!-- badges: end -->

The goal of researchr is to make finding information about funded research opportunities easier and more accessible. This package takes a year as an input and will return a dataframe of information on funded NIH research opportunities from that year. Details include PIs, location, department, and much more.  

## Installation

You can install researchr like so:

```
remotes::install_github('kbruncati/diviiproject')
```

## Data Examples

Here are some basic examples to show what data `nih_research` returns to the user:

```{r}
class(nih_research(1999))

colnames(nih_research(1999)) 
```

## ExPORTER Data Dictionary

If you need more information on a column in your NIH Research dataset, check out the [ExPORTER Data Dictionary](https://report.nih.gov/exporter-data-dictionary).

## Visualization Examples

Here is a sample interactive data visualization posing median total project costs against length of funding for 1999:

```{r}
median_total_cost(data2)
```

Here is another interactive data visualization that shows frequency of funding by state for 1999:

```{r}
#funding_frequency(data2) this doesnt currently work for some reason...
```

## Authors

Benjamin Bruncati and Hongtong Lin
