---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# researchr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/kbruncati)](https://CRAN.R-project.org/package=researchr)
<!-- badges: end -->

The goal of researchr is to make finding information about funded research opportunities easier and more accessible. This package takes a year as an input and will return a dataframe of information on funded NIH research opportunities from that year. Details include PIs, location, department, and much more.  

## Installation

You can install researchr like so:

```
remotes::install_github('kbruncati/diviiproject')
```

## Example

Here are some basic examples to show what `data_return` returns to the user:

```{r example}
library(researchr)

class(nih_research(2002))

ncol(nih_research(1999))  

colnames(nih_research(1999))[-1] 
```

## Authors

Benjamin Bruncati and Hongtong Lin
